\TheTitle

### 2016-04-25 linvis.tex
Adding citation to Reingold Tilford trees

\evantodo{we need a reference to these trees}

@@

The Reingold-Tilford tree (Figures \ref{fig:zoomed_tree} and \ref{fig:tree}) allows the visualization and navigation
of the entire merge-tree in an intuitive representation of the tree. This illustrates a clear notion of
root and leaves, and how to navigate in either direction. Some of the merge trees are very large (figure \ref{fig:zoomed_tree}), containing
thousands of commits and merges. While the tree is capable of producing a
visualization, it becomes much more difficult to understand. For example the merge 73287a43cc79ca06629a88d1a199cd283f42456a performed by Linus Torvalds in May
1, 2013, merged 1722 non-merge commits and 91 merges. footnote{This commit can be inspected at \url{http://li.turingmachine.org/commits/73287a43cc79ca06629a88d1a199cd283f42456a}}

>>>>

@@

The Reingold-Tilford tree\cite{Reingold1981} (Figures \ref{fig:zoomed_tree} and \ref{fig:tree}) allows the visualization and navigation
of the entire merge-tree in an intuitive representation of the tree. This illustrates a clear notion of
root and leaves, and how to navigate in either direction. Some of the merge trees are very large (figure \ref{fig:zoomed_tree}), containing
thousands of commits and merges. While the tree is capable of producing a
visualization, it becomes much more difficult to understand. For example the merge 73287a43cc79ca06629a88d1a199cd283f42456a performed by Linus Torvalds in May
1, 2013, merged 1722 non-merge commits and 91 merges. footnote{This commit can be inspected at \url{http://li.turingmachine.org/commits/73287a43cc79ca06629a88d1a199cd283f42456a}}
